Simultaneous segmentation and distortion correction on diffusion weighted MR using shape priors

### 2012-12-19 Publications/2013-IPMI/Latex/03-Introduction.tex
adding a few references for the technical state of the art

In this paper we propose a novel registration framework to simultaneously
solve the segmentation and distortion challenges, by exploiting as strong 
shape-prior the detailed anatomy extracted from anatomical \ac{mri}. On
one hand, the significant benefits of exploiting the anatomical \ac{mri}
have been demonstrated \cite{zollei_improved_2010}, justifying the use
of the shape prior information. On the other, the
significant coupling between both problems demands for consistent
segmentation, parcellation, and distortion. This need is satisfied by
the use of a unique underlying model of our joint approach.
We reformulate the segmentation problem as an inverse problem, where
we seek for an underlying deformation field (the distortion) mapping 
from the structural space into the diffusion space.

>>>>

\textbf{FIXME: talk about inherent coupling}
The significant benefits of exploiting the anatomical \ac{mri}
have been demonstrated \cite{zollei_improved_2010}, justifying the use
of the shape prior information. This need is satisfied by
the use of a unique underlying model of our joint approach.

\textbf{FIXME: talk about SOA in joint reg-seg, shape-prior registration, atlas-based registration in more general}
\citep{Chan2005,Bresson2006a,Cremers2006,Rousson2002,Schmid2008,Vemuri2003a,Gastaud2004,McInerney1996,Chan,Paragios2003,Ayvaci2007,Pohl2005,Wyatt2003,Yezzi2003,Wang2006,Soatto2002,Yezzi2001,Pohl2006,Chen2002,le_guyader_combined_2011}

\textbf{FIXME: now introduce our own approach}
In this paper we propose a novel registration framework to simultaneously
solve the segmentation and distortion challenges, by exploiting as strong 
shape-prior the detailed anatomy extracted from anatomical \ac{mri}. 
We reformulate the segmentation problem as an inverse problem, where
we seek for an underlying deformation field (the distortion) mapping 
from the structural space into the diffusion space.

\textbf{Now quickly summarize structure of the paper}
